Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-22 paper.tex
results

\begin{table}
\caption{Average precision, recall and f-measure scores on test folds.}
\label{table:results}
\centering
\begin{tabular}{|l|c c c|c c c|}
  \hline
                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
  \textbf{Description} & \textit{P} & \textit{R} & \textit{F} & \textit{P} & \textit{R} & \textit{F}\\
  \hline
  \hline
  Baseline & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
  \hline
  Blocking SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
  Blocking Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
  Blocking NYSIIS & 0.9875 & 0.9826 & 0.9850 & 0.9936 & 0.9814 & 0.9875 \\
  Blocking Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
  \hline
\end{tabular}
\end{table}

\textit{Baseline.} Results presented in this section are all discussed with
respect to a baseline solution using the following combination of components:
\begin{itemize}
\item Blocking: same surname and the same first given name initial strategy;
\item Linkage function: all 22 features defined in Table~\ref{table:features},
    gradient boosted regression trees as supervised learning algorithm
    and a training set of pairs built by balancing easy and difficult cases.
\item Clustering: agglomerative clustering using average linkage and
    block cuts found to maximize $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
\end{itemize}

>>>>

\begin{table}
\caption{Average precision, recall and f-measure scores on test folds.}
\label{table:results}
\centering
\begin{tabular}{|l|c c c|c c c|}
  \hline
                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
  \textbf{Description} & \textit{P} & \textit{R} & \textit{F} & \textit{P} & \textit{R} & \textit{F}\\
  \hline
  \hline
Baseline & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
\hline
Blocking = SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
Blocking = NYSIIS & 0.9875 & 0.9826 & 0.9850 & 0.9936 & 0.9814 & 0.9875 \\
Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
\hline
Classifier = GBRT & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
Classifier = Random Forests & 0.9909 & 0.9783 & 0.9846 & 0.9957 & 0.9752 & 0.9854 \\
Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
\hline
Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711 & 0.9756 & 0.9629 & 0.9692 \\
Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786 & 0.9850 & 0.9707 & 0.9778 \\
Training pairs = Blocked, balanced & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
\hline
Clustering = Average linkage & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671 & 0.9543 & 0.9626 & 0.9584 \\
Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785 & 0.9920 & 0.9688 & 0.9803 \\
\hline
No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
Global cut & -- & -- & -- & -- & -- & -- \\
Block cut & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
\hline
No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
  \hline
\end{tabular}
\end{table}

\textit{Baseline.} Results presented in this section are all discussed with
respect to a baseline solution using the following combination of components:
\begin{itemize}
\item Blocking: same surname and the same first given name initial strategy (SFI);
\item Linkage function: all 22 features defined in Table~\ref{table:features},
    gradient boosted regression trees as supervised learning algorithm
    and a training set of pairs built by balancing easy and difficult cases.
\item Clustering: agglomerative clustering using average linkage and
    block cuts found to maximize $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
\end{itemize}
